Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-05-16 supplementary_material.tex
merge with master and change to png

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{\small{Source inversions for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  }}
  \label{fig:source_correction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
  \caption{\small{Adjoint tomography workflow.}}
  \label{fig:adjoint_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
  \caption{\small{Sub-workflow workflow for preprocessing seismic data.}}
  \label{fig:preprocess_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.pdf}
  \caption{\small{PSF test for Yellowstone.
  A 100~km diameter negative Gaussian anomaly is placed at a depth of 300~km beneath Yellowstone.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_yellowstone}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
  \label{fig:psf_easter}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/afar.pdf}
  \caption{\small{PSF test for Afar.
    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_afar}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/su.pdf}
  \caption{\small{PSF test for Sumatra.
    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_su}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.pdf}
  \caption{\small{PSF test for the middle of the United States.
    A 160~km diameter negative Gaussian anomaly is placed at a depth of 500~km beneath the middle of the US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_mid}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15 ($V_\textrm{sv}$, left column) and GLAD-M25 ($V_\textrm{sv}$; right column).
  The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1,000~km.
  (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.
  }}
  \label{fig:m15_hotspot}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/compare_M15/subduction.pdf}
  \caption{\small{ Vertical cross sections for various subduction regions, same as Fig.~\ref{fig:m15_hotspot}.
  (a) Cocos; (b) India; (c) Sumatra; (d) Fiji-Tonga; (e) Farallon; (f) Scotia. }}
  \label{fig:m15_subduction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{\small{Map views of global shear wavespeed perturbations at various depths for  model
  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
  At a given radius,
  perturbations are calculated relative to each model's average.
  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
  The green circles denote locations of various
  hotspots~\citep{montelli2006catalogue}.
  The range of the colorbar is the same for each row,
  and its maximum value is indicated in parentheses on the left, after
  the depth.}}
  \label{fig:global-vs}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{\small{Map views of global compressional wavespeed variations at various depths for model
  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
  GAP-P4~\citep[right column;][]{fukao2013subducted}.
  For LLNL-G3Dv3, depth ranges are labeled in the bottom right
  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}}
\label{fig:global-vp}
\centering
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{\small{Map views of isotropic shear wavespeed variations beneath North America 
  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
  models. Green circles denote the locations of hotspots. For SL2013NA, we
  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}}
\label{fig:america-vs}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
  \caption{\small{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}}
\label{fig:europe-vs}
\centering
\end{figure}

@@

\begin{figure}[ht!]
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
  \caption{\small{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
  global models S362ANI$+$M (second column) and SL2013sv (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}}
  \label{fig:asia-vs}
  \centering
\end{figure}

@@

\begin{figure}[ht!] 
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}
  \label{fig:southamerica-vp}
  \centering
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.png}
  \caption{\small{Source inversions for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  }}
  \label{fig:source_correction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.png}
  \caption{\small{Adjoint tomography workflow.}}
  \label{fig:adjoint_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.png}
  \caption{\small{Sub-workflow workflow for preprocessing seismic data.}}
  \label{fig:preprocess_workflow}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.png}
  \caption{\small{PSF test for Yellowstone.
  A 100~km diameter negative Gaussian anomaly is placed at a depth of 300~km beneath Yellowstone.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_yellowstone}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.png}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
  \label{fig:psf_easter}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/afar.png}
  \caption{\small{PSF test for Afar.
    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_afar}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/su.png}
  \caption{\small{PSF test for Sumatra.
    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_su}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_mid.png}
  \caption{\small{PSF test for the middle of the United States.
    A 160~km diameter negative Gaussian anomaly is placed at a depth of 500~km beneath the middle of the US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_mid}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.png}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.png}
  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15 ($V_\textrm{sv}$, left column) and GLAD-M25 ($V_\textrm{sv}$; right column).
  The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1,000~km.
  (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.
  }}
  \label{fig:m15_hotspot}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/compare_M15/subduction.png}
  \caption{\small{ Vertical cross sections for various subduction regions, same as Fig.~\ref{fig:m15_hotspot}.
  (a) Cocos; (b) India; (c) Sumatra; (d) Fiji-Tonga; (e) Farallon; (f) Scotia. }}
  \label{fig:m15_subduction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.png}
  \caption{\small{Map views of global shear wavespeed perturbations at various depths for  model
  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic},
  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
  At a given radius,
  perturbations are calculated relative to each model's average.
  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
  The green circles denote locations of various
  hotspots~\citep{montelli2006catalogue}.
  The range of the colorbar is the same for each row,
  and its maximum value is indicated in parentheses on the left, after
  the depth.}}
  \label{fig:global-vs}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.png}
  \caption{\small{Map views of global compressional wavespeed variations at various depths for model
  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl}, and
  GAP-P4~\citep[right column;][]{fukao2013subducted}.
  For LLNL-G3Dv3, depth ranges are labeled in the bottom right
  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}}
\label{fig:global-vp}
\centering
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.png}
  \caption{\small{Map views of isotropic shear wavespeed variations beneath North America 
  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
  models. Green circles denote the locations of hotspots. For SL2013NA, we
  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}}
\label{fig:america-vs}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.png}
  \caption{\small{Map views of isotropic shear wavespeed variations beneath Europe for model GLAD-M25 (first column), two global model (S362ANI$+$M and S40RTS), and
  one regional model~\citep[EU60;][]{zhu2015seismic}. For EU60, the range of the color
  bar is 4\% at all depths, as indicated in the bottom right bottom of the panels.}}
\label{fig:europe-vs}
\centering
\end{figure}

@@

\begin{figure}[ht!]
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.png}
  \caption{\small{Map views of shear wavespeed variations beneath Asia for GLAD-M25~(first column),
  global models S362ANI$+$M (second column) and SL2013sv (third column), and regional model EARA2014~\citep[last column;][]{chen2015multiparameter}.}}
  \label{fig:asia-vs}
  \centering
\end{figure}

@@

\begin{figure}[ht!] 
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.png}
  \caption{\small{Map views of compressional wavespeed variations beneath South America for GLAD-M25~(first column) and global models S362ANI$+$M~\citep{moulik2014anisotropic} (second column), LLNL-G3Dv3~\citep{simmons2012llnl} (third column), and GAP-P4~\citep{fukao2013subducted} (fourth column).}}
  \label{fig:southamerica-vp}
  \centering
\end{figure}
